---
title: "DevOps Dashboard BETA"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
```

Volumes
===================================== 

Column 
-------------------------------------

### Open Tickets

```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)

t_ticket_open <- read.csv(here::here("Data", "t_ticket_open.csv"), stringsAsFactors = FALSE) %>% 
  filter(COUNT != 0)

p <- ggplot(t_ticket_open, aes(x = CUTPOINT, y = COUNT, group = TICKET)) +
  geom_line(aes(colour = TICKET)) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()
  )


ggplotly(p, tooltip = c("x", "y", "colour")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100)
  )
```


Column 
-------------------------------------

### Tickets Started

```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)

t_ticket_started <- read.csv(here::here("Data", "t_ticket_started.csv"), stringsAsFactors = FALSE) %>% 
  filter(COUNT != 0) 

p <- ggplot(t_ticket_started, aes(x = CREATED_MONTH, y = COUNT, group = TICKET)) +
  geom_line(aes(colour = TICKET)) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()
  )


ggplotly(p, tooltip = c("x", "y", "colour")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100)
  )
```



### Tickets Closed

```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)

t_ticket_closed <- read.csv(here::here("Data", "t_ticket_closed.csv"), stringsAsFactors = FALSE) %>% 
  filter(COUNT != 0)

p <- ggplot(t_ticket_closed, aes(x = CLOSED_MONTH, y = COUNT, group = TICKET)) +
  geom_line(aes(colour = TICKET)) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()
  )


ggplotly(p, tooltip = c("x", "y", "colour")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100)
  )
```



Lead Times
===================================== 

Column 
-------------------------------------

### Total Median Lead Times

```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)

t_leadtime_ticket <- read.csv(here::here("Data", "t_leadtime_ticket.csv"), stringsAsFactors = FALSE)

p <- ggplot(t_leadtime_ticket, aes(x = CLOSED_MONTH, y = LEADTIME, group = TICKET)) +
  geom_line(aes(colour = TICKET)) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()
  )


ggplotly(p, tooltip = c("x", "y", "colour")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100)
  )
```


Column 
-------------------------------------

### Development: Net Median Lead Times (excl. Voting Times)

```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)

t_leadtime_dev_net <- read.csv(here::here("Data", "t_leadtime_dev_net.csv"), stringsAsFactors = FALSE)

p <- ggplot(t_leadtime_dev_net, aes(x = CLOSED_MONTH, y = LEADTIME_NET, group = TICKET)) +
  geom_line(aes(colour = TICKET)) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()
  )


ggplotly(p, tooltip = c("x", "y", "colour")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100)
  )
```



### Development: Ratio of Lead Time Spent on Voting

```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(scales)
library(plotly)

t_leadtime_dev_net <- read.csv(here::here("Data", "t_leadtime_dev_net.csv"), stringsAsFactors = FALSE)

p <- ggplot(t_leadtime_dev_net, aes(x = CLOSED_MONTH, y = VOTING_RATIO, group = TICKET)) +
  geom_line(aes(colour = TICKET)) +
  scale_y_continuous(labels = percent) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()
  )


ggplotly(p, tooltip = c("x", "y", "colour")) %>%
  layout(
    yaxis = list(hoverformat = '.4f'),
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100, l = 40)
  )
```



Conformance
===================================== 

Column
-------------------------------------

### Conform Ticket Ratio Since System Start

```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)
library(dplyr)

t_conf_agg <- read.csv(here::here("Data", "t_conf_agg.csv"), stringsAsFactors = FALSE) %>% 
                group_by(CREATED_YEAR, TICKET, CONFORM) %>% 
                summarize(COUNT = sum(COUNT)) %>% 
                ungroup() %>%
                group_by(CREATED_YEAR, TICKET) %>% 
                mutate(CONFORM_PROP = round(COUNT / sum(COUNT), 4)) %>% 
                ungroup() %>% 
                filter(CONFORM == "Conform")

p <- ggplot(t_conf_agg, aes(x = TICKET, y = CONFORM_PROP)) +
  geom_bar(aes(fill = as.factor(CREATED_YEAR)), stat = "identity", position = "dodge") +
  # Need to set text position by 'y' argument as plotly does not handle aes(vjust=)
  #geom_text(aes(label=paste(CONFORM_PROP*100,"%",sep=""), y = CONFORM_PROP+0.01), position = position_dodge(width = 0.6)) +
  scale_y_continuous(labels = percent) +
  theme(
    axis.text.x = element_text(angle = 0),
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()
  )

ggplotly(p, tooltip = c("x", "y", "colour")) %>%
  layout(
    yaxis = list(hoverformat = '.4f'),
    margin = list(l = 40, b = 80),
    legend = list(orientation = "v", y = 0.5)
  )
```    


### Conform/Deviant Ticket Count by Start Month
```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)

t_conf_agg <- read.csv(here::here("Data", "t_conf_agg.csv"), stringsAsFactors = FALSE)

p <- ggplot(t_conf_agg, aes(x = CREATED_MONTH, y = COUNT, fill = CONFORM)) +
  geom_bar(stat = "identity") +
  facet_grid(.~TICKET) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()
  )

ggplotly(p, tooltip = c("x", "y")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 80)
  )
```    


Column
-------------------------------------

### Conform Tickets Lead Time Breakdown (Median)
```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)

t_conf_agg_lt <- read.csv(here::here("Data", "t_conf_agg_lt.csv"), stringsAsFactors = FALSE) %>%
  mutate(SEGMENT = forcats::fct_relevel(SEGMENT, "RELEASE_DAYS", "DEMAND_DAYS", "PRE_DEMAND_DAYS"))

p <- ggplot(t_conf_agg_lt, aes(x = CREATED_MONTH, y = LEAD_TIME, fill = SEGMENT)) +
  geom_bar(stat = "identity") +
  facet_grid(.~TICKET) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()
  )

ggplotly(p, tooltip = c("x", "y")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 80)
  )
```

### Ticket Navigator (Inspect Tickets One-by-One)
```{r, warning=FALSE, message=FALSE}
library(DT)

t_conf <- read.csv(here::here("Data", "t_conf.csv"), stringsAsFactors = FALSE)

datatable(t_conf, rownames = FALSE, extensions = "Buttons", options = list(
  dom = "Bfrtip",
  buttons = list("excel", "csv")
))# %>%
  #formatStyle(colnames(t_conf), fontSize = "70%")
```    


FTE
===================================== 

Column {.tabset}
-------------------------------------

### FTE
```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)

t_fte_ticket <- read.csv(here::here("Data", "t_fte_ticket.csv"), stringsAsFactors = FALSE)

p <- ggplot(t_fte_ticket, aes(x = TARGET_MONTH, y = FTE, group = TICKET)) +
  geom_line(aes(colour = TICKET)) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()
  )

ggplotly(p, tooltip = c("x", "y", "colour")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100)
  )
```


### FTE %
```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)

t_fte_ticket <- read.csv(here::here("Data", "t_fte_ticket.csv"), stringsAsFactors = FALSE)

p <- ggplot(t_fte_ticket, aes(x = TARGET_MONTH, y = FTE_PCT, group = TICKET)) +
  geom_line(aes(colour = TICKET)) +
  scale_y_continuous(labels = percent) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()
  )

ggplotly(p, tooltip = c("x", "y", "colour")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100, l = 40)
  )
```

### FTE/Ticket
```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)

t_fte_ticket <- read.csv(here::here("Data", "t_fte_ticket.csv"), stringsAsFactors = FALSE) 

p <- ggplot(t_fte_ticket, aes(x = TARGET_MONTH, y = FTE_NORM, group = TICKET)) +
  geom_line(aes(colour = TICKET)) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.title = element_blank(),
    axis.title.y = element_blank(),
    axis.title.x = element_blank()
  ) 

ggplotly(p, tooltip = c("x", "y", "colour")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100)
  )
```




Column {.tabset}
-------------------------------------

### Development FTE
```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)
library(scales)

t_fte_phases <- read.csv(here::here("Data", "t_fte_phases.csv"),
  stringsAsFactors = FALSE
) %>%
  mutate(ACTIONTYPEGROUP = forcats::fct_relevel(factor(ACTIONTYPEGROUP),
    "Egyéb",
    after = Inf
  ))

p <- ggplot(t_fte_phases, aes(x = TARGET_MONTH, y = FTE, group = ACTIONTYPEGROUP)) +
  geom_line(aes(colour = ACTIONTYPEGROUP)) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.title = element_blank(),
    axis.title.y = element_blank(),
    axis.title.x = element_blank()
  ) +
  facet_grid(.~TICKET)

ggplotly(p, tooltip = c("x", "y", "colour")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100)
  )
```


### Development FTE %
```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)
library(scales)

t_fte_phases <- read.csv(here::here("Data", "t_fte_phases.csv"),
  stringsAsFactors = FALSE
) %>%
  mutate(ACTIONTYPEGROUP = forcats::fct_relevel(factor(ACTIONTYPEGROUP),
    "Egyéb",
    after = Inf
  ))

p <- ggplot(t_fte_phases, aes(x = TARGET_MONTH, y = FTE_PCT, group = ACTIONTYPEGROUP)) +
  geom_line(aes(colour = ACTIONTYPEGROUP)) +
  scale_y_continuous(labels = percent) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.title = element_blank(),
    axis.title.y = element_blank(),
    axis.title.x = element_blank()
  ) +
  facet_grid(.~TICKET)

ggplotly(p, tooltip = c("x", "y", "colour")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100, l = 40)
  )
```


### Development FTE/Ticket
```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)
library(scales)

t_fte_phases <- read.csv(here::here("Data", "t_fte_phases.csv"),
  stringsAsFactors = FALSE
) %>%
  mutate(ACTIONTYPEGROUP = forcats::fct_relevel(factor(ACTIONTYPEGROUP),
    "Egyéb",
    after = Inf
  ))

p <- ggplot(t_fte_phases, aes(x = TARGET_MONTH, y = FTE_NORM, group = ACTIONTYPEGROUP)) +
  geom_line(aes(colour = ACTIONTYPEGROUP)) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.title = element_blank(),
    axis.title.y = element_blank(),
    axis.title.x = element_blank()
  ) +
  facet_grid(.~TICKET)

ggplotly(p, tooltip = c("x", "y", "colour")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100)
  )
```




Teams
===================================== 

Column {.tabset}
-------------------------------------

### Open Tickets
```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)

t_backlog_ticket_team <- read.csv(here::here("Data", "t_backlog_ticket_team.csv"), stringsAsFactors = FALSE)

p <- ggplot(t_backlog_ticket_team, aes(x = CUTPOINT, y = COUNT, group = APPGROUP)) +
  geom_line(aes(colour = APPGROUP)) +
  facet_grid(.~TICKET) +
  theme(
   axis.text.x = element_text(angle = 90, size = 6),
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    strip.text.x = element_text(size = 10, angle = 0, face = "bold")
  )


ggplotly(p, tooltip = c("x", "y", "colour")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100)
  )
```   



### Tickets Started
```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)

t_nb_ticket_team <- read.csv(here::here("Data", "t_nb_ticket_team.csv"), stringsAsFactors = FALSE)

p <- ggplot(t_nb_ticket_team, aes(x = CREATED_MONTH, y = COUNT, group = APPGROUP)) +
  geom_line(aes(colour = APPGROUP)) +
  facet_grid(.~TICKET) +
  theme(
    axis.text.x = element_text(angle = 90, size = 6),
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    strip.text.x = element_text(size = 10, angle = 0, face = "bold")
  )


ggplotly(p, tooltip = c("x", "y", "colour")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100)
  )
```    



### Tickets Closed
```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)

t_throughput_ticket_team <- read.csv(here::here("Data", "t_throughput_ticket_team.csv"), stringsAsFactors = FALSE)

p <- ggplot(t_throughput_ticket_team, aes(x = CLOSED_MONTH, y = COUNT, group = APPGROUP)) +
  geom_line(aes(colour = APPGROUP)) +
  facet_grid(.~TICKET) +
  theme(
    axis.text.x = element_text(angle = 90, size = 6),
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    strip.text.x = element_text(size = 10, angle = 0, face = "bold")
  )


ggplotly(p, tooltip = c("x", "y", "colour")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100)
  )
```    



### Lead Time
```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)

t_throughputtime_ticket_team <- read.csv(here::here("Data", "t_throughputtime_ticket_team.csv"), stringsAsFactors = FALSE)

p <- ggplot(t_throughputtime_ticket_team, aes(x = CLOSED_MONTH, y = THROUGHPUT_TIME, group = APPGROUP)) +
  geom_line(aes(colour = APPGROUP)) +
  facet_grid(.~TICKET) +
  theme(
    axis.text.x = element_text(angle = 90, size = 6),
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    strip.text.x = element_text(size = 10, angle = 0, face = "bold")
  )


ggplotly(p, tooltip = c("x", "y", "colour")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100)
  )
```


### FTE
```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)

t_fte_ticket_team <- read.csv(here::here("Data", "t_fte_ticket_team.csv"), stringsAsFactors = FALSE)

p <- ggplot(t_fte_ticket_team, aes(x = TARGET_MONTH, y = FTE, group = USERORG_WORKTIMESHEET)) +
  geom_line(aes(colour = USERORG_WORKTIMESHEET)) +
  facet_grid(.~TICKET) +
  theme(
    axis.text.x = element_text(angle = 90, size = 6),
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    strip.text.x = element_text(size = 10, angle = 0, face = "bold")
  )

ggplotly(p, tooltip = c("x", "y", "colour")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100)
  )
```


### FTE/Ticket
```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)

t_fte_ticket_team <- read.csv(here::here("Data", "t_fte_ticket_team.csv"), stringsAsFactors = FALSE)

p <- ggplot(t_fte_ticket_team, aes(x = TARGET_MONTH, y = FTE_NORM, group = USERORG_WORKTIMESHEET)) +
  geom_line(aes(colour = USERORG_WORKTIMESHEET)) +
  facet_grid(.~TICKET) +
  theme(
    axis.text.x = element_text(angle = 90, size = 6),
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    strip.text.x = element_text(size = 10, angle = 0, face = "bold")
  )

ggplotly(p, tooltip = c("x", "y", "colour")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100)
  )
```



Leader Board
===================================== 

Column {.tabset}
-------------------------------------

### Longest Open Tickets
```{r}
library(kableExtra)

t_lb_tp_open <- read.csv(here::here("Data", "t_lb_tp_open.csv"), stringsAsFactors = FALSE)

t_lb_tp_open %>%
  select(-TICKET) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, fixed_thead = T) %>%
  pack_rows(t_lb_tp_open[1, 1], 1, 10, label_row_css = "background-color: #666; color: #fff;") %>%
  pack_rows(t_lb_tp_open[11, 1], 11, 20, label_row_css = "background-color: #666; color: #fff;") %>%
  pack_rows(t_lb_tp_open[21, 1], 21, 30, label_row_css = "background-color: #666; color: #fff;") %>%
  pack_rows(t_lb_tp_open[31, 1], 31, 40, label_row_css = "background-color: #666; color: #fff;") %>% 
 pack_rows(t_lb_tp_open[41, 1], 41, 50, label_row_css = "background-color: #666; color: #fff;") %>%
  pack_rows(t_lb_tp_open[51, 1], 51, 60, label_row_css = "background-color: #666; color: #fff;") 
```



### Highest FTE Open Tickets
```{r}
library(kableExtra)

t_lb_fte_open <- read.csv(here::here("Data", "t_lb_fte_open.csv"), stringsAsFactors = FALSE) %>% filter(TICKET != "Development-RFC") 

t_lb_fte_open %>% 
  select(-TICKET) %>%
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, fixed_thead = T) %>% 
  pack_rows(t_lb_fte_open[1, 1], 1, 10, label_row_css = "background-color: #666; color: #fff;") %>%
  pack_rows(t_lb_fte_open[11, 1], 11, 20, label_row_css = "background-color: #666; color: #fff;") %>%
  pack_rows(t_lb_fte_open[21, 1], 21, 30, label_row_css = "background-color: #666; color: #fff;") %>%
  pack_rows(t_lb_fte_open[31, 1], 31, 40, label_row_css = "background-color: #666; color: #fff;")%>% 
 pack_rows(t_lb_tp_open[41, 1], 41, 50, label_row_css = "background-color: #666; color: #fff;")
#%>%
#  pack_rows(t_lb_tp_open[51, 1], 51, 60, label_row_css = "background-color: #666; color: #fff;") 
```