---
title: "DevOps Dashboard BETA"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
```

Volumes
===================================== 

Column 
-------------------------------------

### New Ticket Count (Number of Created Tickets in Month)

```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)

t_nb_ticket <- read.csv(here::here("Data", "t_nb_ticket.csv"), stringsAsFactors = FALSE)

p <- ggplot(t_nb_ticket, aes(x = CREATED_MONTH, y = NEW_TICKET, group = TICKET)) +
  geom_line(aes(colour = TICKET)) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()
  )


ggplotly(p, tooltip = c("x", "y", "colour")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100)
  )
```



### Throughput Count (Number of Closed Tickets in Month)

```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)

t_throughput_ticket <- read.csv(here::here("Data", "t_throughput_ticket.csv"), stringsAsFactors = FALSE)

p <- ggplot(t_throughput_ticket, aes(x = CLOSED_MONTH, y = THROUGHPUT, group = TICKET)) +
  geom_line(aes(colour = TICKET)) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()
  )


ggplotly(p, tooltip = c("x", "y", "colour")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100)
  )
```



Column 
-------------------------------------

### Backlog Count (Number of Open Tickets on First Day of Month)

```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)

t_backlog_ticket <- read.csv(here::here("Data", "t_backlog_ticket.csv"), stringsAsFactors = FALSE)

p <- ggplot(t_backlog_ticket, aes(x = CUTPOINT, y = BACKLOG, group = TICKET)) +
  geom_line(aes(colour = TICKET)) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()
  )


ggplotly(p, tooltip = c("x", "y", "colour")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100)
  )
```



### Throughput Time (Median Lead-Time of Closed Tickets in Days)

```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)

t_throughputtime_ticket <- read.csv(here::here("Data", "t_throughputtime_ticket.csv"), stringsAsFactors = FALSE)

p <- ggplot(t_throughputtime_ticket, aes(x = CLOSED_MONTH, y = THROUGHPUT_TIME, group = TICKET)) +
  geom_line(aes(colour = TICKET)) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()
  )


ggplotly(p, tooltip = c("x", "y", "colour")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100)
  )
```



FTE
===================================== 

Column
-------------------------------------

### FTE

```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)

t_fte_ticket <- read.csv(here::here("Data", "t_fte_ticket.csv"), stringsAsFactors = FALSE)

p <- ggplot(t_fte_ticket, aes(x = MONTH_WORKTIMESHEET, y = FTE, group = TICKET)) +
  geom_line(aes(colour = TICKET)) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()
  )

ggplotly(p, tooltip = c("x", "y", "colour")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100)
  )
```



### Development FTE (DEV, SDEV, RFC)

```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)

t_fte_phases <- read.csv(here::here("Data", "t_fte_phases.csv"), stringsAsFactors = FALSE)

p <- ggplot(t_fte_phases, aes(x = MONTH_WORKTIMESHEET, y = FTE, group = FTE_BREAKDOWN)) +
  geom_line(aes(colour = FTE_BREAKDOWN)) +
  #facet_grid(.~TICKET) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.title = element_blank(),
    axis.title.y = element_blank(),
    axis.title.x = element_blank()
  )

ggplotly(p, tooltip = c("x", "y", "colour")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100)
  )
```



Column
-------------------------------------

### FTE/Ticket

```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)

t_fte_ticket <- read.csv(here::here("Data", "t_fte_ticket.csv"), stringsAsFactors = FALSE)

p <- ggplot(t_fte_ticket, aes(x = MONTH_WORKTIMESHEET, y = FTE_NORM, group = TICKET)) +
  geom_line(aes(colour = TICKET)) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.title = element_blank(),
    axis.title.y = element_blank(),
    axis.title.x = element_blank()
  ) 

ggplotly(p, tooltip = c("x", "y", "colour")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100)
  )
```



### Development FTE/Ticket (DEV, SDEV, RFC)

```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)

t_fte_phases <- read.csv(here::here("Data", "t_fte_phases.csv"), stringsAsFactors = FALSE)

p <- ggplot(t_fte_phases, aes(x = MONTH_WORKTIMESHEET, y = FTE_NORM, group = FTE_BREAKDOWN)) +
  geom_line(aes(colour = FTE_BREAKDOWN)) +
  #facet_grid(.~TICKET) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.title = element_blank(),
    axis.title.y = element_blank(),
    axis.title.x = element_blank()
  )

ggplotly(p, tooltip = c("x", "y", "colour")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100)
  )
```



Teams
===================================== 

Column {.tabset}
-------------------------------------
   

### New Ticket

```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)

t_nb_ticket_team <- read.csv(here::here("Data", "t_nb_ticket_team.csv"), stringsAsFactors = FALSE)

p <- ggplot(t_nb_ticket_team, aes(x = CREATED_MONTH, y = NEW_TICKET, group = APPGROUP)) +
  geom_line(aes(colour = APPGROUP)) +
  facet_grid(.~TICKET) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    strip.text.x = element_text(size = 12, face = "bold")
  )


ggplotly(p, tooltip = c("x", "y", "colour")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100)
  )
```    




### Backlog

```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)

t_backlog_ticket_team <- read.csv(here::here("Data", "t_backlog_ticket_team.csv"), stringsAsFactors = FALSE)

p <- ggplot(t_backlog_ticket_team, aes(x = CUTPOINT, y = BACKLOG, group = APPGROUP)) +
  geom_line(aes(colour = APPGROUP)) +
  facet_grid(.~TICKET) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    strip.text.x = element_text(size = 12, face = "bold")
  )


ggplotly(p, tooltip = c("x", "y", "colour")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100)
  )
```   
 
### Throughput

```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)

t_throughput_ticket_team <- read.csv(here::here("Data", "t_throughput_ticket_team.csv"), stringsAsFactors = FALSE)

p <- ggplot(t_throughput_ticket_team, aes(x = CLOSED_MONTH, y = THROUGHPUT, group = APPGROUP)) +
  geom_line(aes(colour = APPGROUP)) +
  facet_grid(.~TICKET) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    strip.text.x = element_text(size = 12, face = "bold")
  )


ggplotly(p, tooltip = c("x", "y", "colour")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100)
  )
```    

### Throughput time

```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)

t_throughputtime_ticket_team <- read.csv(here::here("Data", "t_throughputtime_ticket_team.csv"), stringsAsFactors = FALSE)

p <- ggplot(t_throughputtime_ticket_team, aes(x = CLOSED_MONTH, y = THROUGHPUT_TIME, group = APPGROUP)) +
  geom_line(aes(colour = APPGROUP)) +
  facet_grid(.~TICKET) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    strip.text.x = element_text(size = 12, face = "bold")
  )


ggplotly(p, tooltip = c("x", "y", "colour")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100)
  )
```
 
### FTE
    
```{r}
library(ggplot2)
library(plotly)

t_fte_ticket_team <- read.csv(here::here("Data", "t_fte_ticket_team.csv"), stringsAsFactors = FALSE)

p <- ggplot(t_fte_ticket_team, aes(x = MONTH_WORKTIMESHEET, y = FTE, group = USERORG_WORKTIMESHEET)) +
  geom_line(aes(colour = USERORG_WORKTIMESHEET)) +
  facet_grid(.~TICKET) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    strip.text.x = element_text(size = 12, face = "bold")
  )

ggplotly(p, tooltip = c("x", "y", "colour")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100)
  )
```



### FTE/Ticket

```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)

t_fte_ticket_team <- read.csv(here::here("Data", "t_fte_ticket_team.csv"), stringsAsFactors = FALSE)

p <- ggplot(t_fte_ticket_team, aes(x = MONTH_WORKTIMESHEET, y = FTE_NORM, group = USERORG_WORKTIMESHEET)) +
  geom_line(aes(colour = USERORG_WORKTIMESHEET)) +
  facet_grid(.~TICKET) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.title = element_blank(),
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    strip.text.x = element_text(size = 12, face = "bold")
  )

ggplotly(p, tooltip = c("x", "y", "colour")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100)
  )
```



### Development FTE
    
```{r}
library(ggplot2)
library(plotly)

t_fte_phases_team <- read.csv(here::here("Data", "t_fte_phases_team.csv"), stringsAsFactors = FALSE)

p <- ggplot(t_fte_phases_team, aes(x = MONTH_WORKTIMESHEET, y = FTE, group = USERORG_WORKTIMESHEET)) +
  geom_line(aes(colour = USERORG_WORKTIMESHEET)) +
  facet_grid(.~FTE_BREAKDOWN) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    strip.text.x = element_text(size = 12, face = "bold")
  )

ggplotly(p, tooltip = c("x", "y", "colour")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100)
  )
```



### Development FTE/Ticket
    
```{r}
library(ggplot2)
library(plotly)

t_fte_phases_team <- read.csv(here::here("Data", "t_fte_phases_team.csv"), stringsAsFactors = FALSE)

p <- ggplot(t_fte_phases_team, aes(x = MONTH_WORKTIMESHEET, y = FTE_NORM, group = USERORG_WORKTIMESHEET)) +
  geom_line(aes(colour = USERORG_WORKTIMESHEET)) +
  facet_grid(.~FTE_BREAKDOWN) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    strip.text.x = element_text(size = 12, face = "bold")
  )

ggplotly(p, tooltip = c("x", "y", "colour")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100)
  )
```



Conformance
===================================== 

Column
-------------------------------------

### Conform Ticket Count by Create Month (Closed Development [DEV] and Development Small [DEV-VIP, SDEV] Tickets)
```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)

t_conf_agg <- read.csv(here::here("Data", "t_conf_agg.csv"), stringsAsFactors = FALSE)

p <- ggplot(t_conf_agg, aes(x = CREATED_MONTH, y = COUNT, fill = CONFORM)) +
  geom_bar(stat = "identity") +
  facet_grid(.~TICKET) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()
  )

ggplotly(p, tooltip = c("x", "y")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100)
  )
```    

### Conform Ticket **Cumulative** Count by Create Month (Closed Development [DEV] and Development Small [DEV-VIP, SDEV] Tickets)

```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)

t_conf_agg <- read.csv(here::here("Data", "t_conf_agg.csv"), stringsAsFactors = FALSE)

p <- ggplot(t_conf_agg, aes(x = CREATED_MONTH, y = CUMULATIVE_COUNT, fill = CONFORM)) +
  geom_bar(stat = "identity") +
  facet_grid(.~TICKET) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()
  )

ggplotly(p, tooltip = c("x", "y")) %>%
  layout(
    legend = list(orientation = "v", y = 0.5),
    margin = list(b = 100)
  )
```    

Column
-------------------------------------

### Conformance Criteria (Closed Development [DEV] and Development Small [DEV-VIP, SDEV] Tickets)
```{r, warning=FALSE, message=FALSE}
library(DT)

t_conf <- read.csv(here::here("Data", "t_conf.csv"), stringsAsFactors = FALSE)

datatable(t_conf, rownames = FALSE, extensions = "Buttons", options = list(
  dom = "Bfrtip",
  buttons = list("excel", "csv")
))# %>%
  #formatStyle(colnames(t_conf), fontSize = "70%")
```    



Leader Board
===================================== 

Column {.tabset}
-------------------------------------

### Longest Open Tickets
```{r}
library(kableExtra)

t_lb_tp_open <- read.csv(here::here("Data", "t_lb_tp_open.csv"), stringsAsFactors = FALSE)

t_lb_tp_open %>%
  select(-TICKET) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, fixed_thead = T) %>%
  pack_rows(t_lb_tp_open[1, 1], 1, 10, label_row_css = "background-color: #666; color: #fff;") %>%
  pack_rows(t_lb_tp_open[11, 1], 11, 20, label_row_css = "background-color: #666; color: #fff;") %>%
  pack_rows(t_lb_tp_open[21, 1], 21, 30, label_row_css = "background-color: #666; color: #fff;") %>%
  pack_rows(t_lb_tp_open[31, 1], 31, 40, label_row_css = "background-color: #666; color: #fff;")
```



### Highest FTE Open Tickets
```{r}
library(kableExtra)

t_lb_fte_open <- read.csv(here::here("Data", "t_lb_fte_open.csv"), stringsAsFactors = FALSE)

t_lb_fte_open %>% 
  select(-TICKET) %>%
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F, fixed_thead = T) %>% 
  pack_rows(t_lb_fte_open[1, 1], 1, 10, label_row_css = "background-color: #666; color: #fff;") %>%
  pack_rows(t_lb_fte_open[11, 1], 11, 20, label_row_css = "background-color: #666; color: #fff;") %>%
  pack_rows(t_lb_fte_open[21, 1], 21, 30, label_row_css = "background-color: #666; color: #fff;") %>%
  pack_rows(t_lb_fte_open[31, 1], 31, 40, label_row_css = "background-color: #666; color: #fff;")
```
